---
title: "basic steps of linear regression"
author: "ruo"
date: "Thursday, April 09, 2015"
output: word_document
---

Step 1: read the data into R studio
```{r}
setwd=("C:/Users/Ruo/Documents/R")
fueleff<-read.csv("C:/Users/Ruo/Documents/R/FuelEfficiency.csv")
```

step2 :learn the basic info about the dataset. There is highly corralition between some virables, which means we need to drop some of them. 

```{r}
head(fueleff)
cor(fueleff)
```
from the graphs, we could know there is some variables showing linear regression relationship to the observation. We can try it!

```{r, echo=FALSE}
par(mfrow = c(2,2))
plot(GPM~.,data=fueleff)
```

step3: build model initally 
```{r}
model.full<-lm(GPM~.,data=fueleff)
summary(model.full)
```

step4:select variables
1)all-subsets regression
```{r}
library(leaps)
leaps=regsubsets(GPM~.,data=fueleff,nbest=2,nvmax=7)# 2 best model for each number of predictors
out=summary(leaps)
tab=cbind(out$which,out$rsq,out$adjr2,out$cp)
tab
```
The resulting table shows the trade-off between model size and model fit
```{r, echo=FALSE}
plot(leaps, scale="adjr2")
```
we got MPG+NC+HP+ET

2)stepwise method.forward stepwise and backward stepwise
```{r}
library(MASS)
full.model<-lm(GPM~.,data=fueleff)
reduced.model<-step(full.model,direction="backward")

min.model <- lm(GPM~1,data=fueleff)
forward.model<-step(min.model,direction="forward",scope=(~MPG + WT + DIS + NC + HP + ACC + ET))
```

the best AIC is -123.44  GPM ~ MPG + NC + HP + ET

step5: build model
Then we try lm with MPG + NC + HP + ET
```{r}
model.2<-lm(GPM~MPG + NC + HP + ET,data=fueleff)
summary(model.2)
```

Adjusted R-squared:  0.9743 ,even better then the ARS of the model with all variables, which is 0.9722

step6:model validation
```{r}
par(mfrow = c(2,2)) 
plot(model.2,which=c(1:4))
```